---
title: "Results from Experiment 6"
execute: 
  echo: false
page-layout: full
---

**DISCLAIMER: This is an example of what the results will look like.**

You can find here the results from Experiment 6 carried on by Renaud Foucart and Elias Bouacida. Remember that 1 point in the experiment is \$0.02.

The procedure selected by most participants in the experiment is PROCEDURE XX for the participants in the first table and YY for those in the second table. 
The draws of the DC-3 lottery of XX were 2, 9, 8, the variable amount received for participants are:

- 90 points for a TYPE A participant in the GREEN GROUP;
- 20 points for a TYPE A participant in the BLUE GROUP;
- 90 points for a TYPE B participant in the GREEN GROUP;
- 20 points for a TYPE B participant in the BLUE GROUP.

The DC-2 lottery of XX were 5, 1, so the question selected is the fifth one. Those who chose the sure amount will receive 15 points, the others 0 points.

```{r settings}
source(file.path("..", 'Payments.R'))
name <- c('Lottery', 'Market')
column_names <- c("Code", "Type", "Points", "USD", "Vote for Procedure", "Compensation Asked", "Group", "Blue Compensation", "Procedure", "Collective", "About Procedures", "Lottery")
above_header <- c("About You" = 2, "Payments" = 2, "Procedures" = 3, "Procedure Payments" = 3, "Expectations" = 1, " " =1)
```

```{r firstresults}
data1 <- show_payments(name, dir = file.path('..', 'Data'))

kable(data1, col.names = column_names, align='c') %>%
  add_header_above(above_header) %>% 
  kable_styling(fixed_thead = TRUE)
```

For these participants, Procedure 1 and 2 are reversed.

```{r reverseresults}
data2 <- show_payments(rev(name), dir = file.path('..', 'Data'))

kable(data2, col.names = column_names, align='c') %>%
  add_header_above(above_header) %>% 
  kable_styling(fixed_thead = TRUE)
```