---
title: "Results from Experiment 1"
execute: 
  echo: false
page-layout: full
---

You can find here the results from Experiment 1 carried on by Renaud Foucart and Elias Bouacida. Remember that 1 point in the experiment is \$0.02.

The procedure selected by most participants in the experiment is PROCEDURE XX. The draws of the DC-3 lottery of XX were 2, 8, 3, the variable amount received for participants are:

- 80 points for a TYPE A participant in the GREEN GROUP;
- 20 points for a TYPE A participant in the BLUE GROUP;
- 80 points for a TYPE B participant in the GREEN GROUP;
- 20 points for a TYPE B participant in the BLUE GROUP.

The DC-2 lottery of XX were 3, 0, so the question selected is the third one. Those who chose the sure amount will receive 9 points, the others 0 points.

```{r settings}
source(file.path("..", "..", "PreferenceProcedure", "Code", 'Payments','Payments.R'))
name <- c('Lottery', 'Market')
column_names <- c("Code", "Type", "Points", "USD", "Vote for Procedure", "Compensation Asked", "Group", "Blue Compensation", "Procedure", "Collective", "About Procedures", "Lottery")
above_header <- c("About You" = 2, "Payments" = 2, "Procedures" = 3, "Procedure Payments" = 3, "Expectations" = 1, " " =1)
```

```{r firstresults}
data1 <- show_payments(name, dir = file.path("..", "..", "PreferenceProcedure", "Code", 'Payments'))

kable(data1, col.names = column_names, align='c') %>%
  add_header_above(above_header) %>% 
  kable_styling(fixed_thead = TRUE)
```

For these participants, Procedure 1 and 2 are reversed.

```{r reverseresults}
data2 <- show_payments(rev(name), dir = file.path("..", "..", "PreferenceProcedure", "Code", 'Payments'))

kable(data2, col.names = column_names, align='c') %>%
  add_header_above(above_header) %>% 
  kable_styling(fixed_thead = TRUE)
```