---
title: "Results from Experiment 1"
execute: 
  echo: false
  warning: false
page-layout: full
---

```{r settings}
library(scales)
library(dplyr)
library(stringr)
library(kableExtra)
```


```{r draws}

dc2 <- 49
dc3 <- 328
dc4 <- 9666
dc5 <- 78854

above_header <- c("About You" = 2, " " = 1, "About the Mechanisms" = 6,  "Predictions" = 3)
```


You can find here the results from Experiment 1 carried on by Renaud Foucart and Elias Bouacida. 

The different draws of the DC-Lottery of August 16 at 12.50pm are:

- DC-2:  4, 9. The participant number selected is 49;
- DC-3: 3, 2, 8, the rest in the division by 200 is `r dc3 %% 200`, which is the threshold amount (in cents). The first number is below 5, so the question used is the first (and the threshold amount does not matter).
- DC-4: 9, 6, 6, 6, so the rest in the division by 3 is `r dc4%%3` and the question for predictions selected is the first one.
- DC-5: 7, 8, 8, 5, 4, so the sequence to match is Odd, Even, Even, Odd, Even.

Due to a mistake in the implementation of the experiment, you are in group of approximately 50 participants, instead of the 100 originally intended.
In each group, the mechanism chosen to compute the reward may be different.


```{r expe1}
results <- list()
for(i in 1:6){
  data <- read.csv(file = file.path(file.path('..', 'Data', paste0('2023ResultsExperiment1Group', i,'.csv'))))
  
  data <- data %>% 
    mutate(payment = scales::dollar_format()(payment), 
           your_threshold = scales::dollar_format()(your_threshold)) %>% 
    rename_with( ~ str_to_title(gsub("_", " ", .x, fixed = TRUE))) %>% 
    rename_with( ~ gsub("Rps", "RPS", .x, fixed = TRUE))
  results[[i]] <- data
}  
  
  

```

The selected mechanism to attribute the reward in Group 1 is Rock, Paper, Scissors.
The choices of all members of Group 1 are below.

```{r}
kable(results[[1]],
      align= 'c') %>% 
  add_header_above(above_header)
```

The selected mechanism to attribute the reward in Group 2 is Rock, Paper, Scissors.
The choices of all members of Group 2 are below.

```{r}
kable(results[[2]],
      align= 'c') %>% 
  add_header_above(above_header)
```

The selected mechanism to attribute the reward in Group 2 is Rock, Paper, Scissors.
The choices of all members of Group 3 are below.

```{r}
kable(results[[3]],
      align= 'c') %>% 
  add_header_above(above_header)
```

The selected mechanism to attribute the reward in Group 4 is Rock, Paper, Scissors.
The choices of all members of Group 4 are below.

```{r}
kable(results[[4]],
      align= 'c') %>% 
  add_header_above(above_header)
```

The selected mechanism to attribute the reward in Group 5 is Rock, Paper, Scissors.
The choices of all members of Group 5 are below.

```{r}
kable(results[[5]],
      align= 'c') %>% 
  add_header_above(above_header)
```



The selected mechanism to attribute the reward in Group 6 is Rock, Paper, Scissors.
The choices of all members of Group 6 are below.

```{r}
kable(results[[6]],
      align= 'c') %>% 
  add_header_above(above_header)
```